---
title: "Codes for Incidental findings in HBM (JESEE)"
author: "Franco Catuogno"
format: html
---


```{r setup}
#| include: false
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Required packages
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)
library(ggplot2)
library(patchwork)
library(tibble)
library(forcats)
library(openxlsx)
```

# Importing and reshaping datasets
```{r}
rfd_iris <- read_excel("data/IRIS_RfD_simple_list_alpha.xlsx") |>  # RfD values downloaded from: https://iris.epa.gov/AtoZ/alpha/
  select(2,3,7) |> 
  rename(rfd = `RfD (Chronic)`) |> 
  mutate(rfd = str_remove(rfd, "mg/kg-day"),
         rfd = str_replace(rfd, " x 10 ", "e"),
         rfd = as.numeric(rfd)) |> 
  filter(!is.na(rfd))


luxchildren_134detchem <- read_excel("data/Lux2021_NA_CAS_134.xlsx")
  
```

# Approach 1: Ranking cases based on toxicity and concentration:

### Data preparation: identifying which of the 134 chemicals have RfD values
```{r}
rfd_134chems <- inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN") |> 
  select(1:3) |> 
  arrange(rfd)
```


### First, sorting in increasing order of RfD: the higher the RfD the less toxic the chemical.
### Second, sorting in decreasing order of concentration.
```{r}
ranking_approach1 <-  inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN")|> # merging IRIS RfD values with the levels of the 134 chemicals detected in hair of 218 Luxembourgish children
  mutate(rank_RfD = min_rank(rfd), # ranking matched chemicals by RfD values
         ranked_chemicals = str_c(rank_RfD, Chemical, sep = "° ")) |> 
  relocate(ranked_chemicals,rfd, .after = "CAS_RN") |> # relocating rank and RfD value for easier visualization
  arrange(rfd) |> # sorting chemicals by increasing value of RfD (ranking order)
  pivot_longer(cols = 6:223, 
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(rfd, desc(pg_mg)) |> # sort cases in increasing order of rfd and decreasing order of concentration
  mutate(Chemical = recode(Chemical,
                           "Heptachlor-exo-epoxide" = "Heptachlor-epoxide"),
         cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach1 = row_number()) |> # assigning ranking position based on the order
  select(10,9, 7, 5, 8, 4) # selecting the most relevant columns
  
```


# Approach 2: Ranking cases based on concentration
```{r}
ranking_approach2 <-  luxchildren_134detchem |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(desc(pg_mg)) |> # sorting cases in decreasing order of concentration
  mutate(cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach2 = rank(-pg_mg, ties.method = "min")) |> # assigning ranking position based on the concentration levels and giving same rank to same values
  select(6, 5, 3, 1, 4) # selecting the most relevant columns
  
```

# Approach 3: Ranking cases based on the ratio: concentration/median 
```{r}
ranking_approach3 <-  luxchildren_134detchem |> 
  rowwise() |> # to ensure application of operations per row
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE), # computing the minimum detected value for each chemical
         df = round(mean(!is.na(c_across(3:220))) * 100, 2), # computing detection frequencies for each chemical
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by LOD/2
         median_val = median(c_across(3:220), na.rm = TRUE), # computing median value per chemical
         across(3:220, ~ . / median_val)) |> # dividing each value by the median value of the corresponding chemical (rowwise)
  ungroup() |> # to remove the application of operations per row
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_median") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
          rank_approach3 = rank(-conc_median, ties.method = "min")) |> 
  arrange(desc(conc_median)) |> 
  select(9, 8, 6, 1, 7, 4)

```

# Approach 4: Ranking cases based on the ratio: concentration/minimum-detected
```{r}
ranking_approach4 <-  luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         across(3:220, ~ . / lod)) |> 
  ungroup() |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_min") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
         rank_approach4 = rank(-conc_min, ties.method = "min")) |> 
  arrange(rank_approach4) |> 
  select(8, 7, 5, 1, 6, 4)

```

# Exporting the rankings for the Supplementary Material
```{r}
Rankings <- list(
  Approach1_RfDConc = ranking_approach1,
  Approach2_Conc = ranking_approach2,
  Approach3_ConcMedianRatio = ranking_approach3,
  Approach3_ConcMinRatio = ranking_approach4
)

write.xlsx(Rankings, file = "Supplementary_material.xlsx")
```

# Rankings visualization (Figure 1)

## Assigning colors to chemicals

```{r}
colors_Chems <- c("Bisphenol A" = "#1f77b4", "Permethrin" = "#2ca02c", "Bisphenol S" = "#ff7f0e", "Imidacloprid" = "#d62728", 
                 "Metribuzin" = "#9467bd", "Fipronil" = "#8c564b", "Flusilazole" = "#e377c2", "Heptachlor-epoxide" = "#98FB98",
                 "DMST" = "#dbdb8d", "Aldrin" = "#ff9896", "Isoproturon" = "#c49c94", "Cyprodinil" = "#f7b6d2", 
                 "Heptachlor" = "#50C878", "Prochloraz" = "#17becf", "Metoxuron" = "#008080", "Cyhalothrin" = "#DAA520", "Azoxystrobin" = "#800080")
```

## Plotting rankings

```{r}
ranking_approach1 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach1, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1,2,3), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_text(size = 18),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 1, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 1",
       x = "Concentration (pg/mg)",
       y = "Top 20 priority cases") -> ra1

ranking_approach2 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach2, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(10000, 20000, 30000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(10000, 20000, 30000),
                     labels = c("10000", "", "30000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 2",
       x = "Concentration (pg/mg)") -> ra2

ranking_approach3 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach3, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_median, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1000, 2000, 3000, 4000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(1000, 2000, 3000, 4000),
                     labels = c("", "2000", "", "4000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 3",
       x = "Concentration/Median") -> ra3

ranking_approach4 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach4, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_min, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(25000, 100000,200000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(2e4, 1e5, 2e5),
                     labels = c("2e4", "1e5", "2e5")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 4",
       x = "Concentration/MIN") -> ra4

ra1 + ra2 + ra3 + ra4 + plot_layout(nrow = 1)
```

