---
title: "Codes for Incidental findings in HBM (JESEE)"
author: "Franco Catuogno"
format: html
---


```{r setup}
#| include: false
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Required packages
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)
```

# Importing and reshaping datasets
```{r}
rfd_iris <- read_excel("data/IRIS_RfD_simple_list_alpha.xlsx") |>  # IRIS list with RfDs values
  select(2,3,7) |> 
  rename(rfd = `RfD (Chronic)`) |> 
  mutate(rfd = str_remove(rfd, "mg/kg-day"),
         rfd = str_replace(rfd, " x 10 ", "e"),
         rfd = as.numeric(rfd)) |> 
  filter(!is.na(rfd))


luxchildren_134detchem <- read_excel("data/Lux2021_NA_CAS_134.xlsx")
  
```

# Approach 1: Ranking cases based on toxicity and concentration:

### Data preparation: identifying which of the 134 chemicals have RfD values
```{r}
rfd_134chems <- inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN") |> 
  select(1:3) |> 
  arrange(rfd)
```


### First, sorting in increasing order of RfD: the higher the RfD the less toxic the chemical.
### Second, sorting in decreasing order of concentration.
```{r}
ranking_approach1 <-  inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN")|> # merging IRIS RfD values with the levels of the 134 chemicals detected in hair of 218 Luxembourgish children
  mutate(rank_RfD = min_rank(rfd), # ranking matched chemicals by RfD values
         ranked_chemicals = str_c(rank_RfD, Chemical, sep = "° ")) |> 
  relocate(ranked_chemicals,rfd, .after = "CAS_RN") |> # relocating rank and RfD value for easier visualization
  arrange(rfd) |> # sorting chemicals by increasing value of RfD (ranking order)
  pivot_longer(cols = 6:223, 
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(rfd, desc(pg_mg)) |> # sort cases in increasing order of rfd and decreasing order of concentration
  mutate(Chemical = recode(Chemical,
                           "Heptachlor-exo-epoxide" = "Heptachlor-epoxide"),
         cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach1 = row_number()) |> # assigning ranking position based on the order
  select(10,9, 7, 5, 8, 4) # selecting the most relevant columns
  
```


# Approach 2: Ranking cases based on concentration
```{r}
ranking_approach2 <-  luxchildren_134detchem |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(desc(pg_mg)) |> # sorting cases in decreasing order of concentration
  mutate(cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach2 = rank(-pg_mg, ties.method = "min")) |> # assigning ranking position based on the concentration levels and giving same rank to same values
  select(6, 5, 3, 1, 4) # selecting the most relevant columns
  
```

# Approach 3: Ranking cases based on the ratio: concentration/median 
```{r}
ranking_approach3 <-  luxchildren_134detchem |> 
  rowwise() |> # to ensure application of operations per row
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE), # computing the minimum detected value for each chemical
         df = round(mean(!is.na(c_across(3:220))) * 100, 2), # computing detection frequencies for each chemical
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by LOD/2
         median_val = median(c_across(3:220), na.rm = TRUE), # computing median value per chemical
         across(3:220, ~ . / median_val)) |> # dividing each value by the median value of the corresponding chemical (rowwise)
  ungroup() |> # to remove the application of operations per row
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_median") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
          rank_approach3 = rank(-conc_median, ties.method = "min")) |> 
  arrange(desc(conc_median)) |> 
  select(9, 8, 6, 1, 7, 4)


```

# Approach 4: Ranking cases based on the ratio: concentration/minimum-detected
```{r}
ranking_approach4 <-  luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         across(3:220, ~ . / lod)) |> 
  ungroup() |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_min") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
         rank_approach4 = rank(-conc_min, ties.method = "min")) |> 
  arrange(rank_approach4) |> 
  select(8, 7, 5, 1, 6, 4)
```





