---
title: "Codes for Incidental findings in HBM (JESEE)"
author: "Franco Catuogno"
format: html
---


```{r setup}
#| include: false
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Required packages
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)
library(ggplot2)
library(patchwork)
library(tibble)
library(forcats)
```

# Importing and reshaping datasets
```{r}
rfd_iris <- read_excel("data/IRIS_RfD_simple_list_alpha.xlsx") |>  # RfD values downloaded from: https://iris.epa.gov/AtoZ/alpha/
  select(2,3,7) |> 
  rename(rfd = `RfD (Chronic)`) |> 
  mutate(rfd = str_remove(rfd, "mg/kg-day"),
         rfd = str_replace(rfd, " x 10 ", "e"),
         rfd = as.numeric(rfd)) |> 
  filter(!is.na(rfd))


luxchildren_134detchem <- read_excel("data/Lux2021_NA_CAS_134.xlsx")
  
```

# Approach 1: Ranking cases based on toxicity and concentration:

### Data preparation: identifying which of the 134 chemicals have RfD values
```{r}
rfd_134chems <- inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN") |> 
  select(1:3) |> 
  arrange(rfd)
```


### First, sorting in increasing order of RfD: the higher the RfD the less toxic the chemical.
### Second, sorting in decreasing order of concentration.
```{r}
ranking_approach1 <-  inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN")|> # merging IRIS RfD values with the levels of the 134 chemicals detected in hair of 218 Luxembourgish children
  mutate(rank_RfD = min_rank(rfd), # ranking matched chemicals by RfD values
         ranked_chemicals = str_c(rank_RfD, Chemical, sep = "° ")) |> 
  relocate(ranked_chemicals,rfd, .after = "CAS_RN") |> # relocating rank and RfD value for easier visualization
  arrange(rfd) |> # sorting chemicals by increasing value of RfD (ranking order)
  pivot_longer(cols = 6:223, 
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(rfd, desc(pg_mg)) |> # sort cases in increasing order of rfd and decreasing order of concentration
  mutate(Chemical = recode(Chemical,
                           "Heptachlor-exo-epoxide" = "Heptachlor-epoxide"),
         cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach1 = row_number()) |> # assigning ranking position based on the order
  select(10,9, 7, 5, 8, 4) # selecting the most relevant columns
  
```


# Approach 2: Ranking cases based on concentration
```{r}
ranking_approach2 <-  luxchildren_134detchem |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(desc(pg_mg)) |> # sorting cases in decreasing order of concentration
  mutate(cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach2 = rank(-pg_mg, ties.method = "min")) |> # assigning ranking position based on the concentration levels and giving same rank to same values
  select(6, 5, 3, 1, 4) # selecting the most relevant columns
  
```

# Approach 3: Ranking cases based on the ratio: concentration/median 
```{r}
ranking_approach3 <-  luxchildren_134detchem |> 
  rowwise() |> # to ensure application of operations per row
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE), # computing the minimum detected value for each chemical
         df = round(mean(!is.na(c_across(3:220))) * 100, 2), # computing detection frequencies for each chemical
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by LOD/2
         median_val = median(c_across(3:220), na.rm = TRUE), # computing median value per chemical
         across(3:220, ~ . / median_val)) |> # dividing each value by the median value of the corresponding chemical (rowwise)
  ungroup() |> # to remove the application of operations per row
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_median") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
          rank_approach3 = rank(-conc_median, ties.method = "min")) |> 
  arrange(desc(conc_median)) |> 
  select(9, 8, 6, 1, 7, 4)

```

# Approach 4: Ranking cases based on the ratio: concentration/minimum-detected
```{r}
ranking_approach4 <-  luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         across(3:220, ~ . / lod)) |> 
  ungroup() |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_min") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
         rank_approach4 = rank(-conc_min, ties.method = "min")) |> 
  arrange(rank_approach4) |> 
  select(8, 7, 5, 1, 6, 4)

```


# Rankings visualization (Figure 1)

### Assigning colors to chemicals
```{r}
colors_Chems <- c("Bisphenol A" = "#1f77b4", "Permethrin" = "#2ca02c", "Bisphenol S" = "#ff7f0e", "Imidacloprid" = "#d62728", 
                 "Metribuzin" = "#9467bd", "Fipronil" = "#8c564b", "Flusilazole" = "#e377c2", 
                 "Heptachlor-epoxide" = "#98FB98" , "DMST" = "#dbdb8d", "Aldrin" = "#ff9896", "Isoproturon" = "#c49c94", 
                 "Cyprodinil" = "#f7b6d2", "Heptachlor" = "#50C878", "Prochloraz" = "#17becf")

```

### Plotting the rankings
```{r}
ranking_approach1 |> 
  head(10) |> 
  mutate(rank_case = str_c(rank_approach1,cases, sep = "° "),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1,2,3), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 16),
    axis.title.y = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(size = 12, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 1, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 1",
       x = "Concentration (pg/mg)",
       y = "Top 10 priority cases") -> ra1

ranking_approach2 |> 
  head(10) |> 
  mutate(rank_case = str_c(rank_approach2,cases, sep = "° "),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(10000, 20000, 30000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(10000, 20000, 30000),
                     labels = c("10000", "", "30000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 16),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(size = 12, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 2",
       x = "Concentration (pg/mg)") -> ra2

ranking_approach3 |> 
  head(10) |> 
  mutate(rank_case = str_c(rank_approach3,cases, sep = "° "),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_median, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1000, 2000, 3000, 4000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(1000, 2000, 3000, 4000),
                     labels = c("", "2000", "", "4000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 16),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(size = 12, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 3",
       x = "Concentration/Median") -> ra3

ranking_approach4 |> 
  head(10) |> 
  mutate(rank_case = str_c(rank_approach4,cases, sep = "° "),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_min, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(25000, 100000,200000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(25000, 100000,200000),
                     labels = c("25000", "100000", "200000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 16),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 16),
    axis.text.y = element_text(size = 16, hjust = 0.5),
    axis.text.x = element_text(size = 12, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 4",
       x = "Concentration/Minimum") -> ra4

ra1 + ra2 + ra3 + ra4 + plot_layout(nrow = 1)
```


# Exposure profiles

## Population exposure profile of single chemicals (Figure 2)

### Preparation of the dataframe
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         )|> 
  ungroup() |> 
  select(c(3:220)) |> 
  t() |> 
  as.data.frame() |> 
  set_names(luxchildren_134detchem |> 
              pull(Chemical)) |>  
  rownames_to_column(var = "part_id")

chems_params <- luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         max = reduce(c_across(3:220), pmax, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2)) |> 
  ungroup() |> 
  select(1,2,221:223)


chems_params_fig2 <- chems_params |> 
  filter(Chemical == "Permethrin" |
         Chemical == "Fipronil" |
         Chemical == "Bisphenol S" |
         Chemical == "Bisphenol A" |
         Chemical == "Flusilazole" |
         Chemical == "Prochloraz" |
         Chemical == "Aldrin" |
         Chemical == "Heptachlor-exo-epoxide")

abs_min <- chems_params_fig2 |> 
              summarise(min_lod = min(lod, na.rm = TRUE)) |> 
              pull(min_lod)

abs_max <- chems_params_fig2 |> 
              summarise(max_max = max(max, na.rm = TRUE)) |> 
              pull(max_max)

y_axis_limits <- c((abs_min/2), abs_max + 100000)

```


### Population exposure profile of Permethrin (Figure 2A)

#### Preparation of Fig2A parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Permethrin))

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Permethrin < lod) |> 
  summarise(n = n()) |> 
  pull(n)

```

#### Plotting profile for Permethrin
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected permethrin to give different colors
  ggplot(aes(x = part_id, y = Permethrin, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Permethrin",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```

### Population exposure profile of Fipronil (Figure 2B)

#### Preparation of Fig2B parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Fipronil)) # sorting part_id by Fipronil values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Fipronil < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Fipronil
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected Fipronil to give different colors
  ggplot(aes(x = part_id, y = Fipronil, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Fipronil",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```



### Population exposure profile of Bisphenol S (Figure 2C)

#### Preparation of Fig2B parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Bisphenol S`)) # sorting part_id by Bisphenol S values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Bisphenol S` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Bisphenol S
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Bisphenol S` to give different colors
  ggplot(aes(x = part_id, y = `Bisphenol S`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Bisphenol S",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```


### Population exposure profile of Bisphenol A (Figure 2D)

#### Preparation of Fig2D parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Bisphenol A`)) # sorting part_id by Bisphenol A values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Bisphenol A` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Bisphenol A
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Bisphenol A` to give different colors
  ggplot(aes(x = part_id, y = `Bisphenol A`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Bisphenol A",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```




### Population exposure profile of Flusilazole (Figure 2E)

#### Preparation of Fig2E parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Flusilazole)) # sorting part_id by Flusilazole values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Flusilazole < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Flusilazole
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Flusilazole` to give different colors
  ggplot(aes(x = part_id, y = Flusilazole, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Flusilazole",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```



### Population exposure profile of Prochloraz (Figure 2F)

#### Preparation of Fig2F parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Prochloraz)) # sorting part_id by Prochloraz values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Prochloraz < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Prochloraz
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Prochloraz` to give different colors
  ggplot(aes(x = part_id, y = Prochloraz, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Prochloraz",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```


### Population exposure profile of Aldrin (Figure 2G)

#### Preparation of Fig2G parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Aldrin)) # sorting part_id by Aldrin values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Aldrin < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Aldrin
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Aldrin` to give different colors
  ggplot(aes(x = part_id, y = Aldrin, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Aldrin",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```


### Population exposure profile of Heptachlor-exo-epoxide (Figure 2H)

#### Preparation of Fig2H parameters
```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Heptachlor-exo-epoxide`)) # sorting part_id by Heptachlor-exo-epoxide values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Heptachlor-exo-epoxide` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Heptachlor-exo-epoxide
```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Heptachlor-exo-epoxide` to give different colors
  ggplot(aes(x = part_id, y = `Heptachlor-exo-epoxide`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Heptachlor-exo-epoxide",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2)), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0)), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none")
```