---
title: "Codes for Incidental findings in HBM"
author: "Franco Catuogno"
format: html
---


```{r setup}
#| include: false
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Required packages
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(purrr)
library(ggplot2)
library(patchwork)
library(tibble)
library(forcats)
library(openxlsx)
library(ggrepel)
```

# Importing and reshaping datasets
```{r}
rfd_iris <- read_excel("data/IRIS_RfD_simple_list_alpha.xlsx") |>  # RfD values downloaded from: https://iris.epa.gov/AtoZ/alpha/
  select(2,3,7) |> 
  rename(rfd = `RfD (Chronic)`) |> 
  mutate(rfd = str_remove(rfd, "mg/kg-day"),
         rfd = str_replace(rfd, " x 10 ", "e"),
         rfd = as.numeric(rfd)) |> 
  filter(!is.na(rfd))


luxchildren_134detchem <- read_excel("data/Lux2021_NA_CAS_134.xlsx")
  
```

# Approach 1: Ranking cases based on toxicity and concentration:

### Data preparation: identifying which of the 134 chemicals have RfD values
```{r}
rfd_134chems <- inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN") |> 
  select(1:3) |> 
  arrange(rfd)
```


### First, sorting in increasing order of RfD: the higher the RfD the less toxic the chemical.
### Second, sorting in decreasing order of concentration.
```{r}
ranking_approach1 <-  inner_join(rfd_iris, luxchildren_134detchem, by = "CAS_RN")|> # merging IRIS RfD values with the levels of the 134 chemicals detected in hair of 218 Luxembourgish children
  mutate(rank_RfD = min_rank(rfd), # ranking matched chemicals by RfD values
         ranked_chemicals = str_c(rank_RfD, Chemical, sep = "° ")) |> 
  relocate(ranked_chemicals,rfd, .after = "CAS_RN") |> # relocating rank and RfD value for easier visualization
  arrange(rfd) |> # sorting chemicals by increasing value of RfD (ranking order)
  pivot_longer(cols = 6:223, 
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(rfd, desc(pg_mg)) |> # sort cases in increasing order of rfd and decreasing order of concentration
  mutate(Chemical = recode(Chemical,
                           "Heptachlor-exo-epoxide" = "Heptachlor-epoxide"),
         cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach1 = row_number()) |> # assigning ranking position based on the order
  select(10,9, 7, 5, 8, 4) # selecting the most relevant columns
  
```


# Approach 2: Ranking cases based on concentration
```{r}
ranking_approach2 <-  luxchildren_134detchem |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "pg_mg",
               values_drop_na = TRUE) |> # pivoting data in order to build the ranking
  arrange(desc(pg_mg)) |> # sorting cases in decreasing order of concentration
  mutate(cases = str_c(part_id, Chemical, sep = "/"), # creating a variable for the cases: combinations participant/chemical
         rank_approach2 = rank(-pg_mg, ties.method = "min")) |> # assigning ranking position based on the concentration levels and giving same rank to same values
  select(6, 5, 3, 1, 4) # selecting the most relevant columns
  
```

# Approach 3: Ranking cases based on the ratio: concentration/median 
```{r}
ranking_approach3 <-  luxchildren_134detchem |> 
  rowwise() |> # to ensure application of operations per row
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE), # computing the minimum detected value for each chemical
         df = round(mean(!is.na(c_across(3:220))) * 100, 2), # computing detection frequencies for each chemical
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by LOD/2
         median_val = median(c_across(3:220), na.rm = TRUE), # computing median value per chemical
         across(3:220, ~ . / median_val)) |> # dividing each value by the median value of the corresponding chemical (rowwise)
  ungroup() |> # to remove the application of operations per row
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_median") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
          rank_approach3 = rank(-conc_median, ties.method = "min")) |> 
  arrange(desc(conc_median)) |> 
  select(9, 8, 6, 1, 7, 4)

```

# Approach 4: Ranking cases based on the ratio: concentration/minimum-detected
```{r}
ranking_approach4 <-  luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         across(3:220, ~ . / lod)) |> 
  ungroup() |> 
  pivot_longer(cols = 3:220,
               names_to = "part_id",
               values_to = "conc_min") |> 
  mutate(cases = str_c(part_id, Chemical, sep = "/"),
         rank_approach4 = rank(-conc_min, ties.method = "min")) |> 
  arrange(rank_approach4) |> 
  select(8, 7, 5, 1, 6, 4)

```

# Exporting the rankings for the Supplementary Material
```{r}
Rankings <- list(
  Approach1_RfDConc = ranking_approach1,
  Approach2_Conc = ranking_approach2,
  Approach3_ConcMedianRatio = ranking_approach3,
  Approach3_ConcMinRatio = ranking_approach4
)

write.xlsx(Rankings, file = "Supplementary_material.xlsx")
```

# Rankings visualization (Figure 1)

## Assigning colors to chemicals

```{r}
colors_Chems <- c("Bisphenol A" = "#1f77b4", "Permethrin" = "#2ca02c", "Bisphenol S" = "#ff7f0e", "Imidacloprid" = "#d62728", 
                 "Metribuzin" = "#9467bd", "Fipronil" = "#8c564b", "Flusilazole" = "#e377c2", "Heptachlor-epoxide" = "#98FB98",
                 "DMST" = "#dbdb8d", "Aldrin" = "#ff9896", "Isoproturon" = "#c49c94", "Cyprodinil" = "#f7b6d2", 
                 "Heptachlor" = "#50C878", "Prochloraz" = "#17becf", "Metoxuron" = "#008080", "Cyhalothrin" = "#DAA520", "Azoxystrobin" = "#800080")
```

## Plotting rankings

```{r}
ranking_approach1 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach1, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1,2,3), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_text(size = 18),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 1, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 1",
       x = "Concentration (pg/mg)",
       y = "Top 20 priority cases") -> ra1

ranking_approach2 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach2, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = pg_mg, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(10000, 20000, 30000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(10000, 20000, 30000),
                     labels = c("10000", "", "30000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 2",
       x = "Concentration (pg/mg)") -> ra2

ranking_approach3 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach3, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_median, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(1000, 2000, 3000, 4000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(1000, 2000, 3000, 4000),
                     labels = c("", "2000", "", "4000")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 3",
       x = "Concentration/Median") -> ra3

ranking_approach4 |> 
  head(20) |> 
  mutate(rank_case = str_c(cases," (", rank_approach4, "°)"),
         rank_case = factor(rank_case, levels = rev(rank_case))) |> 
  ggplot(aes(x = conc_min, y = rank_case, fill = Chemical)) +
  geom_bar(stat = "identity", color = "black", width = 0.7) +
  geom_vline(xintercept = c(25000, 100000,200000), color = "lightgrey", linetype = "dashed", size = 0.5) +
  scale_x_continuous(breaks = c(2e4, 1e5, 2e5),
                     labels = c("2e4", "1e5", "2e5")) +
  scale_fill_manual(values = colors_Chems) +
  theme_minimal() +
  theme(
    text = element_text(family = "Arial", size = 18),
    axis.title.y = element_blank(),
    axis.title.x = element_text(size = 18),
    axis.text.y = element_text(size = 18, hjust = 1),
    axis.text.x = element_text(size = 14, hjust = 0.5),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(color = "black"),
    legend.position = "none",
    plot.margin = margin(1, 1, 1, 0, "cm"),
    plot.title = element_text(hjust = 0.1, size = 20)) +
  labs(title = "Approach 4",
       x = "Concentration/MIN") -> ra4

ra1 + ra2 + ra3 + ra4 + plot_layout(nrow = 1)
```

# Exposure profiles

## Population exposure profile of single chemicals (Figure 2)

### Preparation of the dataframe

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         )|> 
  ungroup() |> 
  select(c(3:220)) |> 
  t() |> 
  as.data.frame() |> 
  set_names(luxchildren_134detchem |> 
              pull(Chemical)) |>  
  rownames_to_column(var = "part_id")

chems_params <- luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         max = reduce(c_across(3:220), pmax, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2)) |> 
  ungroup() |> 
  select(1,2,221:223)


chems_params_fig2 <- chems_params |> 
  filter(Chemical == "Permethrin" |
         Chemical == "Fipronil" |
         Chemical == "Bisphenol S" |
         Chemical == "Bisphenol A" |
         Chemical == "Flusilazole" |
         Chemical == "Prochloraz" |
         Chemical == "Aldrin" |
         Chemical == "Heptachlor-exo-epoxide")

abs_min <- chems_params_fig2 |> 
              summarise(min_lod = min(lod, na.rm = TRUE)) |> 
              pull(min_lod)

abs_max <- chems_params_fig2 |> 
              summarise(max_max = max(max, na.rm = TRUE)) |> 
              pull(max_max)

y_axis_limits <- c((abs_min/2), abs_max + 100000)

```

### Population exposure profile of Permethrin (Figure 2A)

#### Preparation of Fig2A parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Permethrin))

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Permethrin") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Permethrin < lod) |> 
  summarise(n = n()) |> 
  pull(n)

```

#### Plotting profile for Permethrin

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected permethrin to give different colors
  ggplot(aes(x = part_id, y = Permethrin, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Permethrin",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg"), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0), "pg/mg"), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_pmt
```

### Population exposure profile of Fipronil (Figure 2B)

#### Preparation of Fig2B parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Fipronil)) # sorting part_id by Fipronil values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Fipronil") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Fipronil < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Fipronil

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected Fipronil to give different colors
  ggplot(aes(x = part_id, y = Fipronil, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Fipronil",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg"), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0), "pg/mg"), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_fpn
```

### Population exposure profile of Bisphenol S (Figure 2C)

#### Preparation of Fig2B parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Bisphenol S`)) # sorting part_id by Bisphenol S values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol S") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Bisphenol S` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Bisphenol S

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Bisphenol S` to give different colors
  ggplot(aes(x = part_id, y = `Bisphenol S`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Bisphenol S",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg"), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0), "pg/mg"), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_bps
```

### Population exposure profile of Bisphenol A (Figure 2D)

#### Preparation of Fig2D parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Bisphenol A`)) # sorting part_id by Bisphenol A values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Bisphenol A") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Bisphenol A` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Bisphenol A

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Bisphenol A` to give different colors
  ggplot(aes(x = part_id, y = `Bisphenol A`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Bisphenol A",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg"), color = "#D55E00", hjust = 1, vjust = 1) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,0), "pg/mg"), color = "#D55E00", hjust = 1, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_bpa
```

### Population exposure profile of Flusilazole (Figure 2E)

#### Preparation of Fig2E parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Flusilazole)) # sorting part_id by Flusilazole values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Flusilazole") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Flusilazole < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Flusilazole

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Flusilazole` to give different colors
  ggplot(aes(x = part_id, y = Flusilazole, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Flusilazole",
       x = "Participants",
       y = "Concentration in pg/mg (log scale)") +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,4), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,3), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_fsz
```

### Population exposure profile of Prochloraz (Figure 2F)

#### Preparation of Fig2F parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Prochloraz)) # sorting part_id by Prochloraz values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Prochloraz") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Prochloraz < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Prochloraz

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Prochloraz` to give different colors
  ggplot(aes(x = part_id, y = Prochloraz, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Prochloraz",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,4), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,3), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_pcz
```

### Population exposure profile of Aldrin (Figure 2G)

#### Preparation of Fig2G parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, Aldrin)) # sorting part_id by Aldrin values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Aldrin") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(Aldrin < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Aldrin

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Aldrin` to give different colors
  ggplot(aes(x = part_id, y = Aldrin, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Aldrin",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = Inf, y = max, label = paste("MAX =", round(max,2), "pg/mg"), color = "#D55E00", hjust = 3, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,0),"%"), color = "#D55E00", angle = 90, vjust = 1.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_ald
```

### Population exposure profile of Heptachlor-exo-epoxide (Figure 2H)

#### Preparation of Fig2H parameters

```{r}
luxchildren_134detchem_t <- luxchildren_134detchem_t |> 
  mutate(part_id = fct_reorder(part_id, `Heptachlor-exo-epoxide`)) # sorting part_id by Heptachlor-exo-epoxide values

lod <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(lod))
max <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(max))
df <- as.numeric(chems_params_fig2 |>
  filter(Chemical == "Heptachlor-exo-epoxide") |> 
  select(df))

horizontal_lines <- c(lod, max)
nondet_percentil <- 1 - df/100

cutoff_part_id <- luxchildren_134detchem_t |> 
  filter(`Heptachlor-exo-epoxide` < lod) |> 
  summarise(n = n()) |> 
  pull(n)
```

#### Plotting profile for Heptachlor-exo-epoxide

```{r}
luxchildren_134detchem_t |> 
  mutate(color_group = if_else(as.numeric(part_id) <= cutoff_part_id, "left", "right")) |>  # separating participants with detected and non-detected `Heptachlor-exo-epoxide` to give different colors
  ggplot(aes(x = part_id, y = `Heptachlor-exo-epoxide`, color = color_group)) +
  geom_point(size = 2) +
  labs(title = "Heptachlor-exo-epoxide",
       x = "Participants",
       y = element_blank()) +
  scale_y_continuous(trans = 'log10', 
                     limits = y_axis_limits,
                     breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)) +
  scale_color_manual(values = c("left" = "grey", "right" = "#0072B2")) +  
  scale_x_discrete(breaks = function(x) x[seq(1, length(x), by = 30)]) +
  geom_hline(yintercept = lod, linetype = "dashed", color = "#D55E00") +
  geom_hline(yintercept = max, linetype = "dashed", color = "#D55E00") +
  geom_vline(xintercept = cutoff_part_id, linetype = "dashed", color = "#D55E00") +
  annotate("text", x = Inf, y = lod, label = paste("MIN =", round(lod,2), "pg/mg", "= MAX"), color = "#D55E00", hjust = 2, vjust = -0.5) +
  annotate("text", x = cutoff_part_id, y = abs_max - 10000, label = paste("DF=", round(df,1),"%"), color = "#D55E00", angle = 90, vjust = -0.5, hjust = 1) +
  theme_minimal(base_size = 15) +
  theme(plot.title = element_text(size = 20, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = 1),
        axis.text.y = element_text(size = 8),
        panel.grid.major = element_line(color = "grey95", size = 0.5),
        panel.grid.minor = element_line(color = "grey96", size = 0.25),
        legend.position = "none") -> pep_hee
```

### Figure 2: Combination of the 8 plots

```{r}
fig2 <- (pep_pmt | pep_fpn | pep_bps | pep_bpa) / 
  (pep_fsz | pep_pcz | pep_ald | pep_hee) +
  plot_annotation(tag_levels = 'A')
fig2
```


## Chemical exposure profile of single participant (Figure 3)

### Preparation of the dataframe with non-detected values as half of LOD

```{r}
luxchildren_134detchem_ratioconclod <- luxchildren_134detchem |> 
  rowwise() |> 
  mutate(lod = reduce(c_across(3:220), pmin, na.rm = TRUE),
         df = round(mean(!is.na(c_across(3:220)))* 100, 2),
         across(3:220, ~ ifelse(is.na(.), lod/2, as.numeric(.))), # substituting non-detected values (NAs) by lod/2 for later visualization purposes.
         across(3:220, ~ . / lod)) |> 
  ungroup()
```

### Chemical exposure profile of participant S117

#### Especification of S117 data and parameters before plotting 
```{r}
# Preprocess data
plot_data <- luxchildren_134detchem_ratioconclod |> 
  mutate(
    Chemical = forcats::fct_reorder(Chemical, S117),
    Chemical_num = as.numeric(Chemical))

# Definition of the percentile threshold for the y-axis to separate detected of non-detected chemicals 
percentile <- (luxchildren_134detchem |> 
                 summarise(sum(is.na(S117))) |> 
                 pull()
               )/134 # percentage of non-detected chemicals

y_percentile_value <- plot_data |> 
  summarise(q = quantile(Chemical_num, probs = percentile)) |> 
  pull(q)

plot_data <- plot_data |> 
  mutate(
    Status = if_else(
      Chemical_num <= y_percentile_value,
      "Non detected",
      "Detected"))

# Definition of the Maximum Conc/MIN value (x-axis) to harmonize dimensions in all plots 
max_x_value <- plot_data |> 
  summarise(max_val = max(S117)) |> 
  pull(max_val)

```

#### Plotting CEP for participant S117
```{r}

cep_S117 <- plot_data |> 
  ggplot(aes(x = S117, y = Chemical, color = Status)) +
  
    geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +

    geom_hline(
    yintercept = y_percentile_value,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +
  
  annotate(
    "text",
    x = 1.6,
    y = 7,
    label = "Concentration = MIN",
    color = "black",
    hjust = 0.5,
    size = 4,
    angle = 90
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value - 2,
    label = "Non detected",
    color = "#009E73",
    hjust = 1,
    size = 5
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value + 2,
    label = "Detected",
    color = "#D55E00",
    hjust = 1,
    size = 5
  ) +  

 geom_point(size = 3) +

    scale_color_manual(
    values = c(
      "Non detected" = "#009E73",
      "Detected" = "#D55E00"
    ),
    guide = "none"
  ) +

  scale_x_continuous(
    trans = "log10",
    breaks = c(1, 100, 10000),
    limits = c(NA, max_x_value)
  ) +

  scale_y_discrete(
    breaks = function(x) x[seq(1, length(x), by = 1)]
  ) +

  coord_cartesian(
    ylim = c(0.5, nlevels(plot_data$Chemical) + 2)
  ) +

  labs(
    title = "Participant S117",
    x = "Concentration/MIN (log scale)",
    y = NULL
  ) +

  theme_minimal(base_size = 16) +

  theme(
    plot.title = element_text(
      size = 14,
      hjust = 0.5,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 10,
      hjust = 1
    ),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(
      size = 11,
      margin = margin(r = 10)
    ),
    plot.margin = margin(15, 25, 15, 15),
    panel.grid.major = element_line(
      color = "grey90",
      size = 0.5
    ),
    panel.grid.minor = element_blank()
  )

cep_S117
```

### Chemical exposure profile of participant S075

#### Especification of S075 data and parameters before plotting 
```{r}
# Preprocess data
plot_data <- luxchildren_134detchem_ratioconclod |> 
  mutate(
    Chemical = forcats::fct_reorder(Chemical, S075),
    Chemical_num = as.numeric(Chemical))

# Definition of the percentile threshold for the y-axis to separate detected of non-detected chemicals 
percentile <- (luxchildren_134detchem |> 
                 summarise(sum(is.na(S075))) |> 
                 pull()
               )/134 # percentage of non-detected chemicals

y_percentile_value <- plot_data |> 
  summarise(q = quantile(Chemical_num, probs = percentile)) |> 
  pull(q)

plot_data <- plot_data |> 
  mutate(
    Status = if_else(
      Chemical_num <= y_percentile_value,
      "Non detected",
      "Detected"))

# Definition of the Maximum Conc/MIN value (x-axis) to harmonize dimensions in all plots 
max_x_value <- plot_data |> 
  summarise(max_val = max(S117)) |> 
  pull(max_val)

```

#### Plotting CEP for participant S075
```{r}

cep_S075 <- plot_data |> 
  ggplot(aes(x = S075, y = Chemical, color = Status)) +
  
    geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +

    geom_hline(
    yintercept = y_percentile_value,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +
  
  annotate(
    "text",
    x = 1.6,
    y = 7,
    label = "Concentration = MIN",
    color = "black",
    hjust = 0.5,
    size = 4,
    angle = 90
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value - 2,
    label = "Non detected",
    color = "#009E73",
    hjust = 1,
    size = 5
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value + 2,
    label = "Detected",
    color = "#D55E00",
    hjust = 1,
    size = 5
  ) +  

 geom_point(size = 3) +

    scale_color_manual(
    values = c(
      "Non detected" = "#009E73",
      "Detected" = "#D55E00"
    ),
    guide = "none"
  ) +

  scale_x_continuous(
    trans = "log10",
    breaks = c(1, 100, 10000),
    limits = c(NA, max_x_value)
  ) +

  scale_y_discrete(
    breaks = function(x) x[seq(1, length(x), by = 1)]
  ) +

  coord_cartesian(
    ylim = c(0.5, nlevels(plot_data$Chemical) + 2)
  ) +

  labs(
    title = "Participant S075",
    x = "Concentration/MIN (log scale)",
    y = NULL
  ) +

  theme_minimal(base_size = 16) +

  theme(
    plot.title = element_text(
      size = 14,
      hjust = 0.5,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 10,
      hjust = 1
    ),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(
      size = 11,
      margin = margin(r = 10)
    ),
    plot.margin = margin(15, 25, 15, 15),
    panel.grid.major = element_line(
      color = "grey90",
      size = 0.5
    ),
    panel.grid.minor = element_blank()
  )

cep_S075
```

### Chemical exposure profile of participant S045

#### Especification of S045 data and parameters before plotting 
```{r}
# Preprocess data
plot_data <- luxchildren_134detchem_ratioconclod |> 
  mutate(
    Chemical = forcats::fct_reorder(Chemical, S045),
    Chemical_num = as.numeric(Chemical))

# Definition of the percentile threshold for the y-axis to separate detected of non-detected chemicals 
percentile <- (luxchildren_134detchem |> 
                 summarise(sum(is.na(S045))) |> 
                 pull()
               )/134 # percentage of non-detected chemicals

y_percentile_value <- plot_data |> 
  summarise(q = quantile(Chemical_num, probs = percentile)) |> 
  pull(q)

plot_data <- plot_data |> 
  mutate(
    Status = if_else(
      Chemical_num <= y_percentile_value,
      "Non detected",
      "Detected"))

# Definition of the Maximum Conc/MIN value (x-axis) to harmonize dimensions in all plots 
max_x_value <- plot_data |> 
  summarise(max_val = max(S117)) |> 
  pull(max_val)

```

#### Plotting CEP for participant S075
```{r}

cep_S045 <- plot_data |> 
  ggplot(aes(x = S045, y = Chemical, color = Status)) +
  
    geom_vline(
    xintercept = 1,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +

    geom_hline(
    yintercept = y_percentile_value,
    linetype = "dashed",
    color = "black",
    size = 1
  ) +
  
  annotate(
    "text",
    x = 1.6,
    y = 7,
    label = "Concentration = MIN",
    color = "black",
    hjust = 0.5,
    size = 4,
    angle = 90
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value - 2,
    label = "Non detected",
    color = "#009E73",
    hjust = 1,
    size = 5
  ) +

annotate(
    "text",
    x = max_x_value,
    y = y_percentile_value + 2,
    label = "Detected",
    color = "#D55E00",
    hjust = 1,
    size = 5
  ) +  

 geom_point(size = 3) +

    scale_color_manual(
    values = c(
      "Non detected" = "#009E73",
      "Detected" = "#D55E00"
    ),
    guide = "none"
  ) +

  scale_x_continuous(
    trans = "log10",
    breaks = c(1, 100, 10000),
    limits = c(NA, max_x_value)
  ) +

  scale_y_discrete(
    breaks = function(x) x[seq(1, length(x), by = 1)]
  ) +

  coord_cartesian(
    ylim = c(0.5, nlevels(plot_data$Chemical) + 2)
  ) +

  labs(
    title = "Participant S045",
    x = "Concentration/MIN (log scale)",
    y = NULL
  ) +

  theme_minimal(base_size = 16) +

  theme(
    plot.title = element_text(
      size = 14,
      hjust = 0.5,
      face = "bold"
    ),
    axis.text.y = element_text(
      size = 10,
      hjust = 1
    ),
    axis.text.x = element_text(size = 10),
    axis.title.x = element_text(
      size = 11,
      margin = margin(r = 10)
    ),
    plot.margin = margin(15, 25, 15, 15),
    panel.grid.major = element_line(
      color = "grey90",
      size = 0.5
    ),
    panel.grid.minor = element_blank()
  )

cep_S045
```

### Fig 3 of IF_v4
```{r}
fig3 <- (cep_S117 | cep_S075 | cep_S045) 
fig3
```


## Comparision BPA and Fipronil's PEP with background gradient (Figure 4) 

### Preparation of the dataframe
```{r}
# Limiting dataframe to Fipronil
fip_ranking  <- luxchildren_134detchem_t |> 
  select(Fipronil) |> 
  arrange(Fipronil) |> 
  mutate(rank_participant = paste0("rank", row_number()))

# Limiting dataframe to BPA
bpa_ranking  <- luxchildren_134detchem_t |> 
  select(`Bisphenol A`) |> 
  arrange(`Bisphenol A`) |> 
  mutate(rank_participant = paste0("rank", row_number()))

# Combining the 2 dataframes
fip_vs_bpa <- inner_join(fip_ranking, bpa_ranking) |> 
  relocate(rank_participant) |> 
  pivot_longer(2:3, names_to = "Chemical", values_to = "Concentration")  |> 
  group_by(Chemical) |> 
  mutate(rank_participant = factor(rank_participant, levels = rank_participant[order(Concentration)])) |> 
  ungroup()


# Creation of a gradient background for the combined data frame
gradient_bg <- fip_vs_bpa |> 
  summarise(n = n_distinct(rank_participant)) |> 
  mutate(
    x = list(seq_len(n)),
    xend = list(seq_len(n) + 1),
    y = -Inf,
    yend = Inf
  ) |> 
  unnest(c(x, xend)) |> 
  select(x, xend, y, yend)
```

### Plot of the comparision of the 2 PEPs
```{r}

# Defining Fipronil's maximum value for the horizontal dashed line
fip_max <- chems_params_fig2 |>
  filter(Chemical == "Fipronil") |>
  pull(max)

# Preparation of a dataframe for the labels of the dot-plots
label_data <- fip_vs_bpa |>
  group_by(Chemical) |>
  slice_max(rank_participant, n = 1) |>
  ungroup()

# Plot
ggplot() +
  geom_rect(
    data = gradient_bg,
    aes(
      xmin = x - 0.5,
      xmax = xend - 0.5,
      ymin = y,
      ymax = yend,
      fill = x
    ),
    alpha = 0.7,
    inherit.aes = FALSE
  ) +

  scale_fill_gradientn(
    colors = c("#F0F9FF", "#EFF6FF", "#BEDBFF", "#51A2FF", "#193CB8"),
    values = scales::rescale(c(0, 0.80, 0.90, 0.97, 1)),
    name = "Likelihood of impactful personalized intervention",
    breaks = range(gradient_bg$x),
    labels = c("Low", "High")
  ) +

  guides(
    fill = guide_colorbar(
      direction = "horizontal",
      title.position = "top",
      label.position = "bottom",
      barwidth = unit(8, "cm"),
      barheight = unit(0.6, "cm"),
      ticks = FALSE
    ),
    color = "none"
  ) +

  geom_point(
    data = fip_vs_bpa,
    aes(
      x = rank_participant,
      y = Concentration,
      color = Chemical
    ),
    size = 2
  ) +

  coord_trans(y = "log10") +

  scale_y_continuous(
    limits = y_axis_limits,
    breaks = c(0.0001, 0.001, 0.01, 0.1, 1, 10, 100, 1000, 10000)
  ) +

  geom_hline(
    yintercept = fip_max,
    linetype = "dashed",
    color = "black"
  ) +

  geom_text(
    data = label_data,
    aes(
      x = rank_participant + 2,
      y = Concentration,
      label = Chemical,
      color = Chemical
    ),
    hjust = 1.5,
    vjust = 1,
    size = 4,
    fontface = "bold",
    show.legend = FALSE
  ) +

  labs(
    x = "Participants rank",
    y = "Concentration (pg/mg)"
  ) +

  scale_color_manual(
    values = c(
      "Bisphenol A" = "#1f77b4",
      "Fipronil" = "#8c564b"
    )
  ) +

  theme_minimal() +
  theme(legend.position = "top")
```

## Global visualization of the concentration/MIN values fo different cases (Figure 5) 
    Limited to 1000 combinations with only the top 6 chemicals

### Preparation of the dataframe
```{r}
colors_Chems3 <- c(
    "Bisphenol A"   = "#1f77b4",
    "Permethrin"    = "#2ca02c",
    "Bisphenol S"   = "#ff7f0e",
    "Imidacloprid"  = "#d62728",
    "Fipronil"      = "#8c564b",
    "Azoxystrobin"  = "#800080"
)

colors_border <- c(
    "Bisphenol A"   = "#0f4c81",
    "Permethrin"    = "#1c6b1c",
    "Bisphenol S"   = "#cc6600",
    "Imidacloprid"  = "#8b1c1c",
    "Fipronil"      = "#5a3a2a",
    "Azoxystrobin"  = "#4b004b"
)

chem_order <- c(
    "Permethrin",
    "Fipronil",
    "Imidacloprid",
    "Bisphenol S",
    "Bisphenol A",
    "Azoxystrobin"
)

plot_data2 <- ranking_approach4 |>
    filter(Chemical %in% names(colors_Chems3)) |>
    mutate(
        Chemical = factor(Chemical, levels = chem_order),
        x_jitter = 1 + runif(n(), min = -0.002, max = 0.002)
    ) |>
    slice_head(n = 1000)

label_data <- plot_data2 |>
    filter(part_id %in% c("S117", "S075", "S045")) |>
    group_by(part_id) |>
    slice_head(n = 1) |>
    ungroup()

y_min <- plot_data2 |>
    summarise(y_min = min(conc_min, na.rm = TRUE)) |>
    pull(y_min)

y_max <- plot_data2 |>
    summarise(y_max = max(conc_min, na.rm = TRUE)) |>
    pull(y_max)

ggplot(plot_data2, aes(x = x_jitter, y = conc_min)) +
    
    geom_point(
        aes(fill = Chemical, color = Chemical),
        shape = 21,
        stroke = 0.5,
        size = 2.5,
        alpha = 0.8
    ) +
    
    geom_text_repel(
        data = label_data,
        aes(label = part_id, color = Chemical),
        size = 3.4,
        nudge_x = 0.00035,
        direction = "x",
        point.padding = 0.3,
        box.padding = 0.3,
        max.overlaps = Inf,
        show.legend = FALSE
    ) +
    
    scale_y_log10() +
    scale_x_continuous(limits = c(0.9975, 1.0035)) +
    
    scale_fill_manual(values = colors_Chems3) +
    scale_color_manual(values = colors_border) +
    
    annotate(
        "polygon",
        x = c(1.00240, 1.00250, 1.00280, 1.00210),
        y = c(y_min, y_min, y_max, y_max),
        fill = "grey70",
        alpha = 0.6
    ) +
    
    annotate(
        "text",
        x = 1.00240,
        y = y_max * 1.4,
        label = "Higher priority",
        size = 3.4,
        vjust = 0
    ) +
    
    annotate(
        "text",
        x = 1.00240,
        y = y_min / 1.4,
        label = "Lower priority",
        size = 3.5,
        vjust = 1
    ) +
    
    labs(
        x = "Cases (participant/chemical)",
        y = "Concentration/MIN"
    ) +
    
    theme_minimal() +
    theme(
        axis.text.x = element_blank(),
        legend.text = element_text(size = 10),
        legend.title = element_text(size = 11)
    )
```

